### 2013-07-18 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
updating strong scaling figures for new multiple set reduction

Although not as dramatic as one might originally expect from
introducing replication, there are some modest gains in efficiencies
at high core counts by using multiple sets. Of interest here is where
the multiple set cases perform better than the single set case after
the single set case has hit the strong scaling wall. In
Figure~\ref{fig:titan_strong_ms_eff}, at 16,384 cores the single set
case operates at 38\% efficiency while at the same number of cores,
the 2 set case with history replication operates at 62\%
efficiency. This is reasonable improvement in the use of those
computational resources, gained by replicating the problem. Beyond
16,384 cores, there is not a compelling reason to use more
computational resources for the this problem.

>>>>

Although not as dramatic as one might originally expect from
introducing replication, there are some modest gains in efficiencies
at high core counts by using multiple sets. Of interest here is where
the multiple set cases perform better than the single set case after
the single set case has hit the strong scaling wall. In
Figure~\ref{fig:titan_strong_ms_eff}, at 16,384 cores the single set
case operates at 38\% efficiency while at the same number of cores,
the 2 set case with history replication operates at 58\%
efficiency. This is reasonable improvement in the use of those
computational resources, gained by replicating the problem. Beyond
16,384 cores, there is not a compelling reason to use more
computational resources for the this problem.
